---
title: "Cracking Iris Data "
output: html_notebook
---

## 0. Preprocessing Data
```{r}
str(iris)
```

### Add column to divide test and train data
```{r}
set.seed(19731027)
iris$dv = FALSE
iris[sort(sample(nrow(iris), nrow(iris[,])*.8, replace=FALSE)),'dv'] = TRUE
head(iris)
```

### Split Train and Test data
```{r}
iris.train <- iris[iris$dv==TRUE,-6]
iris.test <- iris[iris$dv==FALSE,-6]
nrow(iris.train)
nrow(iris.test)
```

## 1. Multinominal Regression Analysis

### Make Multinomial Model
```{r}
library(nnet)
regression.model <- multinom(Species~.,data=iris.train)
rg.predicted <- predict(regression.model,iris.test)
```

### Make Confusion Matrix
```{r}
table(rg.predicted, iris.test$Species)
```

### Calculate Accuracy with Test Data
```{r}
sum(rg.predicted == iris.test$Species)/nrow(iris.test)
```

## 2.Decision Tree

### Make Decion Tree Model
```{r}
library(rpart)
dt.model <- rpart(Species ~ Sepal.Length + Sepal.Width + Petal.Length + Petal.Width, data=iris.train, method = "class")
dt.predicted <- predict(dt.model,iris.test,type="class")
```

### Make Confusion Matrix
```{r}
table(dt.predicted, iris.test$Species)
```

### Calculate Accuracy with Test Data
```{r}
sum(dt.predicted == iris.test$Species)/nrow(iris.test)
```

### Plot the Decion Tree

#### load mandatory library
```{r, results=FALSE}
library(rpart.plot)
library(RColorBrewer)
library(rattle)
```

```{r}
fancyRpartPlot(dt.model)
```

## 3.KNN

### Make train, test data for knn and train label
```{r}
library(class)
iris.train.label <- iris.train$Species
iris.knn.train <- iris.train[,-5]
iris.knn.test <- iris.test[,-5]
```

### Make Model
```{r}
knn.predicted <- knn(train = iris.knn.train, test = iris.knn.test, cl = iris.train.label, k = 3)
```

### Make Confusion Matrix
```{r}
table(knn.predicted, iris.test$Species)
```

### Calculate Accuracy with Test Data
```{r}
sum(knn.predicted == iris.test$Species)/nrow(iris.test)
```

## 4.Deep Learning with H2o

### Load H2o library
```{r, results=FALSE}
library(h2o)
```

### initialize h2o instance
```{r}
localH2O <- h2o.init(ip = 'localhost', port = 54321, max_mem_size = '4g')
```

### Transfer Iris dataframe to H2o instance 
```{r}
iris.h2o.train <- as.h2o(iris.train, destination_frame = "iris.h2o.train")
iris.h2o.test <- as.h2o(iris.test, destination_frame = "iris.h2o.test")
nrow(iris.h2o.train)
nrow(iris.h2o.test)
```


### Make Gradient Boosted Model
```{r}
model.h2o <- h2o.deeplearning(x=1:4, y=5, training_frame = iris.h2o.train)
h2o.predicted <- h2o.predict(model.h2o, iris.h2o.test)[,"predict"]
```

### Make Confusion Matrix
```{r}
table(as.vector(h2o.predicted), as.vector(iris.h2o.test$Species))
```

### Calculate Accuracy with Test Data
```{r}
sum(as.vector(h2o.predicted) ==  as.vector(iris.h2o.test$Species)) / length(as.vector(iris.h2o.test$Species))
```




































